### 2010-03-11 thesis/SensorMLOnSenseTile/trunk/thesis/SensorMLonSenseTileThesis.tex
updates

\newpage
\subsection{DataProducer}

DataProducer generates observations in Observation xml standard.

@@

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{sensetile_static_diagam.png}}
\caption{DataProducer Static Diagram}\label{fig:sensetile_static_diagam.png}
\end{figure}

Interfaces to the Sensor Board
Use PacketInput stream to access SenseTile observation packets.

\subsubsection{Sensors}

Thermistor components reads out the temperature value
and its output is sent to both the raw data and the celcius
converter component and on to the tuples. System reads packets
and averages them for every configurable seconds. Default 1.
These tuples are sent to webservice provider as observations.

Observation as described in SOS.

@@

SWE not fully web services as W3C might define. Not SOAP. HTTP envelope
flexible.
Streaming the data.

>>>>

\newpage
\subsection{DataProducer}
The DataProducer's role, as described previously, is to read sensor data from the Sensor Board and generate O\&M observations. These observations are then sent to the SOS instance. The processing of the sensor data to generate the observations is described by the SensorML models. The DataProducer uses the OGC Vast Library to instantiate objects that implement the required data processing chains based on the SensorML models. The BON static diagram \ref{fig:bon_static_diagam_producer.png}
 shows the main clusters and classes of the DataProvider.

The SMLEngine cluster contains classes that provide access to
the Vast Lib that is providing the SensorML Engine.  The Vast Lib implemenation
of the SensorML Engine is hidden from the rest of the code thus.

The Sensors and Converters clusters contain classes that provide
implementation of process methods for SensorML components in the SensorBoard and
Converter SensorML Models respectively. These are referred to as sensor objects and
converter objects henceforth.

The DataProducer operates by repeating the below steps continously.
 \begin{enumerate}
\item Read Sensor Board Data
\item Process Sensor Data
\item Create O\&M Observations
\end{enumerate}
The steps above are detailed the in following sections with reference
to the BON static diagram \ref{fig:bon_static_diagam_producer.png}.

\subsubsection {1. Read Sensor Board Data}

The UCD SensorBoard Library is used by DataProducer to access
the data generated by the Sensor Board.
The library provides high level interface to the
the data from the sensor board. It reads data from the Sensor board and generates packets
containing the sensor data. These packets provide functionality
to access a particular sensors data such as the temperature
meaurement generated by the thermistor. 
This library is shown as the SensorBoard cluster in \ref{fig:bon_static_diagam_producer.png}
An instance of the class PacketInputStream to is used access the packets from the Sensor Board.

The DataProducer uses the Observer pattern to provide
packets to the SensorMLEngine for processing.
At start up the SenseTileSystem reads the list of sensor objects from the SMLEngine that
implement the Sensors interface. These objects provide an entry point
to the SensorML processing chain and can read data from the UCD LIB packets.
These sensor objects implement reading strategies for the type of data they read. 
For example the ThermistorSensor reads out the temperature value
but will average it before it sent to the SensorML Engine for processing.

\subsubsection {2. Process Sensor Data}
The PacketInputStream will request the SenseTileSystem to exexcute
the SensorML engine to process the sensor data. The SensoML Enigine
will execute the process chains described in the SenseTile SensorML model.
The sensor objects output will be passed to the coverter objects. The
outputs of both object types are then available to generate observations.

\subsubsection {3. Create O\&M Observations}

When the SensorML Engine is finished
and there are obsevations generated these
need to be sent to the SOS. An O\&M Onservation
xml string containing the data is sent to
the SOS instance. This is timestamped at
this stage.
 containing the output from
the SensorML processes and send the observations
to the SOS.
-register offerings with the SOS. In this design
each system is an offering.
Need to generate an observation model?

Questions.
If have light data but no temp. As temp is only
every 1000 packets?

How to know when to generate observation
for the two offerings?
DataProducer generates observations in Observation xml standard.

@@

\begin{figure}[h]
\scalebox{0.65}{\includegraphics{bon_static_diagam_producer.png}}
\caption{DataProducer Static Diagram}\label{fig:bon_static_diagam_producer.png}
\end{figure}

Interfaces to the Sensor Board

@@

A lot of schemas needed.

SWE not fully web services as W3C might define. Not SOAP. HTTP envelope
flexible.

Vast Lib use as a references only. Other ways such a XQUERY? XML techs?
As there are a large number of types etc. A quick way for a prototype.
Had to update library code to get it to work with the SenseTile Schemas. Schemas
passed the validation test tool from the site.

Portabiltiy, Vast Types POJOs.

Streaming the data.
